Word learning at the semantics pragmatics interface

### 2020-04-20 paper/supplementary_material.Rmd
modify bda figure

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **Integration model** used for *Explanation*. $L_1$ represents the RSA model defined by Eq. 2, used to predict the Combination Data $d^{Ex3}$ from Expt. 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$. This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity parameter $\\rho_i$ (which varies by age). Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt. 1), via the same RSA model with no common ground $L'_1$;  common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt. 2). Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\\beta_0$ and $\\beta_1$, respectively). Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu^{\\theta}$ and $\\sigma^{\\theta}$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}

@@

\node[det, above=of data_me](L1_me){$L_1'$};
\node[det, above=of data_comb](L1_comb){$L_1$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5) { 
$\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
 $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
$\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ \\
$\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
 $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
 $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ \\
 $\mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
 $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ \\
 $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
 $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0)$ \\
$\beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
 $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$
};

>>>>

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **integration model** used for *Explanation*. $RSA$ represents the general model architecture and paremeters defined by Eq. \\@ref(eq:rsabasic1) - \\@ref(eq:rsabasic3). $L_1$ represents the RSA model defined by Eq. \\@ref(eq:rsafull1), used to predict the combination data $d^{Ex3}$ from Expt. 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$. This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age). Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt. 1), via the same RSA model with no common ground $L$; common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt. 2).  Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\\beta_0$ and $\\beta_1$, respectively). Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $\\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}

@@

\node[det, above=of data_me](L1_me){$L'_{1_{ij}}$};
\node[det, above=of data_comb](L1_comb){$L_{1_{ijk}}$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

@@

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5.75) { 
$\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
 $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
 $d^{Ex2}_{i} \sim \text{Bernoulli}(\rho_i)$ \\
 \\
$\beta^\alpha_0 \sim \text{Uniform}(-3,3); \beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
 $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
 \\
 $\mu^\theta_0 \sim \text{Uniform}(-3,3); \mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
 $\sigma^\theta_0 \sim \text{Uniform}(0,2); \sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
 $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0); \beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
 $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$ \\
 $d^{Ex1}_{ij} \sim L'_1,  d^{Ex3}_{ij} \sim L_1$
};
